Embedding Intuitionistic into Classical Logic

### 2023-03-10 LPAR/LPAR-EIICL.tex

An important step in the embedding will be the elimination of quantifiers via Herbrandization.
In this process we introduce fresh variables and add additional function symbols to the signature.
A fresh variable is any variable that does not occur in any considered formula.
Whenever we add a function symbol we implicitly extend the signature by a fresh symbol.

\begin{definition}\label{definition:skolemization}
	For formulas $\varphi$ we define the Skolemization $\varphi^S_Z$ and Herbrandization $\varphi^H_Z$ with respect to a set of free variables $Z$ by simultaneous induction:
	\begin{itemize}
		\item $A^S_Z = A^H_Z = A$ for each atomic $A$.
		\item $(\varphi\circ\psi)^X_Z = \varphi^X_Z\circ\psi^X_Z$ for $\circ\in\{\wedge, \vee\}$, $X\in\{S, H\}$.
		\item $(\varphi\to\psi)^S_Z = \varphi^H_Z\to \psi^S_Z$ and $(\varphi\to\psi)^H_Z = \varphi^S_Z\to\psi^H_Z$.
		\item $(\forall x\varphi)^S_Z = \forall x(\varphi[a/x]^S_{Z\cup\{a\}}[x/a])$ where $a$ is a new free variable.\\$(\forall x\varphi)^H_Z = \varphi[s(z_1,\dots,z_n)/x]^H_Z$ where $s$ is a new function, $\{z_1\dots z_n\} = Z$.
		\item $(\exists x\varphi)^S_Z = \varphi[s(z_1,\dots,z_n)/x]^S_Z$ where $s$ is a new function, $\{z_1\dots z_n\} = Z$.\\$(\exists x\varphi)^H_Z = \exists x(\varphi[a/x]^H_{Z\cup\{a\}}[x/a])$
 where $a$ is a new free variable.
	\end{itemize}
	Let $\varphi^S = (\exists x_1\dots\exists x_n \varphi[x_1/a_1\dots x_n/a_n])^S_\emptyset$ and $\varphi^H = (\forall x_1\dots\forall x_n \varphi[x_1/a_1\dots x_n/a_n])^H_\emptyset$ where $a_1,\dots,a_n$ are the free variables occurring in $\varphi$.
\end{definition}

@@

This is somewhat unsatisfying as we end up in a much more complex logic. However using the normal form from Lemma~\ref{lemma:propositional-normal-form}, i.e. assuming that $\varphi$ is of the form $$\left(\bigwedge\mathcal R\wedge\bigwedge\mathcal X\right)\to P$$ for some flat clauses $\mathcal R$ and implicational clauses $\mathcal X$, further simplification is possible:
\begin{itemize}
	\item For flat clauses $(\bigwedge A_i\to\bigvee B_j)^\nu$ is
	$\forall w\left(\nu\preceq w\to\bigwedge_i A_i(w)\to\bigvee_jB_j(w)\right).$
	\item For implication clauses $((A\to B)\to C)^\nu$ is
	$$\forall w(\nu\preceq w\to(\forall k(w\preceq k\to A(k)\to B(k)))\to C(w))$$
\end{itemize}

and after applying Herbrandization we end up with a formula $$\varphi^{CH} = K(\varphi)\to\left(\bigwedge\mathcal R^{b S}\wedge \bigwedge\mathcal X^{b S}\right)\to P(s)$$ where $s$ is a new constant symbol, each formula in $\mathcal R^{b S}$ is of the form
$$\forall w\left(s\preceq w\to\bigwedge_iA_i(w)\to\bigvee_jB_j(w)\right)$$
and each formula $\psi\in\mathcal X^{b S}$ is of the form
$$\forall w(s\preceq w\to(w\preceq f_\psi(w)\to A(f_\psi(w))\to B(f_\psi(w)))\to C(w))$$
with $f_\psi$ being a new function symbol.
We now argue that if a counter-model for $\varphi^{CH}$ exists then a small counter-model exists. This is ultimately what enables our translations.

\begin{definition}
For $\psi\in\mathcal X$ let $[\psi]$ denote the corresponding clause in $\mathcal X^{b S}$. Suppose we are given a counter-model $\mathcal M = (M, I)$ for $\varphi^{CH}$.
We say $(A\to B)\to C\in\mathcal X$ is \emph{fulfilled} at $m\in M$ iff $A^I(m)\to B^I(m)$ is false or $C^I(m)$ is true. For $\psi\in\mathcal X$ define $$g_\psi : M\to M, m\mapsto\begin{cases}
		m,&\text{ if $\psi$ is fulfilled at $m$,}\\
		f^I_{\lbrack\psi\rbrack}(m),&\text{ else.}		
	\end{cases}$$Define a model $\mathcal M_T = (M_T, I_T)$ as follows:
	\begin{itemize}
		\item $M_T$ is the set of sequences without repetition on $\mathcal X$.
		\item $s^{I_T} = \epsilon$.
		\item Interpret $\preceq$ as the prefix-order.
		\item We set $$f_\psi^{I_T}(\psi_1\dots\psi_n) = \begin{cases}
			\psi_1\dots\psi_n, &\text{if $\psi$ occurs in $[\psi_1]\dots[\psi_n]$,}\\
			\psi_1\dots\psi_n\psi, &\text{else.}			
		\end{cases}$$
		\item For propositional variables $P$, we set $$P^{I_T}\left(\psi_1\dots \psi_n\right) = P^I\left(g_{\psi_n}\left(\dots\left(g_{\psi_1}\left(s^I\right)\right)\dots\right)\right).$$
	\end{itemize}
\end{definition}
\begin{lemma}~\label{thm:prop-countermodel-reduction}
	Let $\mathcal M = (M, I)$ be a counter-model to $\mathcal \varphi^{CH}$.
	\begin{enumerate}
		\item $\psi$ is fulfilled at $f_{[\psi]}^I(m)$ for all $m\in M, \psi\in\mathcal X$.
		\item If $\psi$ is fulfilled at some $m\in M$ then $\psi$ is fulfilled at all $n\succeq^I m$.
	\end{enumerate}
\end{lemma}

\begin{proof}
	1. If $C^I(m)$ is true then we are done due to persistency. Otherwise $C^I(m)$ is false.
	Because $(A^I(f_{[\psi]}^I(m))\to B^I(f_{[\psi]}^I(m)))\to C^I(m)$ holds, then $A^I(f_{[\psi]}^I(m))\to B^I(f_{[\psi]}^I(m))$ must be false.

	2. Let $n\succeq^I m$.
	If $C^I(n)$ is true, we are done.
	Otherwise $C^I(n)$ is false.
	Due to persistency $C^I(m)$ is also false.
	Because $\psi$ is fulfilled at $m$, $A^I(m)\to B^I(m)$ must be false, i.e. $A^I(m)$ is true and $B^I(m)$ is false. Then $A^I(n)$ and $A^I(f^I_{[\psi]}(n))$ are also true due to persistency.
	Because $(A^I(f^I_{[\psi]}(n))\to B^I(f^I_{[\psi]}(n)))\to C^I(n)$ holds, we now get that  $B^I(f^I_{[\psi]}(n))$ must be false.
	But then due to persistency so is $B^I(n)$ and we have that $\psi$ is fulfilled at $n$.
\end{proof}

Essentially what this tells us is that for every $m$ at which $\psi$ is fulfilled, in particular for each $m$ in the image of $f_{[\psi]}$, we may add the assumption that $f_{[\psi]}(n) = n$ for all $n\succeq m$ without changing the validity of $\psi$. With this lemma in hand showing that $(M_T, I_T)$ is a counter-model to $\varphi^{CH}$ is a straightforward check of definitions.

@@

\begin{definition}\label{def:fo-translation}
	Let $\varphi$ be a predicate formula. Define $\varphi^{\nu}$ inductively:
\todo{genau genommen müsstest du noch sagen, dass $\nu$ eine freie Variable ist. Im letzten Fall der Definition benützen wir dann aber w gleichzeitig als freie und gebundene Variable}
	\begin{itemize}
		\item $\bot^\nu = \bot$.
		\item $A(\vec t)^{\nu} = A(\vec t, \nu)$ for every predicate symbol $A$.
		\item $(\varphi\circ\psi)^\nu = \varphi^\nu\circ\psi^u$ for $\circ\in\{\wedge, \vee\}$.
		\item $(\varphi\to \psi)^\nu = \forall w(\nu\preceq w\to\varphi^{w}\to\psi^{w})$.
		\item $(\exists x\varphi)^\nu = \exists x(E(x,\nu)\wedge\varphi[a/x]^\nu[x/a])$ where $a$ is a new free variable.
		\item $(\forall x\varphi)^\nu = \forall w(i\preceq w\to \forall x(E(x, w)\to \varphi[a/x]^w[x/a]))$ where $a$ is a new free variable and $w$ is a new bound variable.
	\end{itemize}
	where $w$ is some new bound variable. Let $K(\varphi)$ encode the theory of Kripke structures as well as the predicate $E$, i.e.
	\begin{align*}
		K(\varphi) = \:& \text{PartialOrder}(\preceq) \wedge \forall u \forall w (u\preceq w\to \text{DomainSubset}(u, w)) \wedge\\
		& \forall u(\text{World(u)}\to \text{DomainClosed}(u))\wedge \forall u\forall w (u\preceq w\to \text{Persistent}(u, w)).
	\end{align*}
	with e.g.:\vspace*{-.76cm}
	\begin{align*}
		\text{PartialOrder}(\preceq) = &\:\forall u(u\preceq u)\wedge\forall u\forall w(u\preceq w\to w\preceq u\to u = w)\wedge\\&\:\forall u\forall v\forall w(u\preceq v\to v\preceq w\to u\preceq w)\\
		\text{DomainSubset}(u, w) = &\:\forall x(E(x, u)\to E(x, w))\\
		\text{World}(u) = &\:\exists xE(x, u)\\
		\text{DomainClosed}(u) = &\:\bigwedge\left\{\forall\vec x(\vec E(\vec x, u)\to E(f(\vec x), u))\:|\:\text{$f$ a function in $\varphi$}\right\}\\
		\text{Persistent}(u, w) = &\:\bigwedge\left\{\forall\vec x(\vec A(\vec x, u)\to A(\vec x, w))\:|\:\text{$A$ a predicate in $\varphi$}\right\}
	\end{align*}
	Then define
	$\varphi^C = K(\varphi)\to\text{World}(b)\to \vec E(\vec a, b)\to \varphi^b$ where $\vec a$ contains all free variables occurring in $\varphi$ and $b$ is a new free variable.
\end{definition}

@@

\begin{wrapfigure}[14]{r}{0.4\textwidth}
	\vspace{6.4cm}
	\hspace*{1.5cm}
	\begin{tikzpicture}
		\begin{scope}[opacity=0.1, blend mode=multiply]
			\def\firstcircle{(90:.75) circle (1.5)}
			\def\secondcircle{(210:.75) circle (1.5)}
			\def\thirdcircle{(330:.75) circle (1.5)}
			\begin{tikzpicture}
				\begin{scope}[shift={(3cm,-5cm)}, fill opacity=0.5]
					\fill[red] \firstcircle;
					\fill[green] \secondcircle;
					\fill[blue] \thirdcircle;
					\draw node {$491$};
					\draw node at (30:1.2) {$30$};
					\draw node at (150:1.2) {$42$};
					\draw node at (270:1.2) {$22$};
					\draw node at (90:1.8) {$8$};
					\draw node at (210:1.8) {$2$};
					\draw node at (330:1.8) {$417$};
				\end{scope}
			\end{tikzpicture}
		\end{scope}
	\end{tikzpicture}
	\vspace*{-7.6cm}
	\caption{Instances proven by combinations of Embedding (red), Embedding (idem.) (green), ileanCoP or nanoCoP (blue)}
	\label{fig:c}
\end{wrapfigure}

\vspace*{-.5cm}
Two versions of the translation were tested, one with and one without the additional axioms encoding idempotence. The results are stated in Figure \ref{fig:a}.
In general, our approach falls short of the state of the art.
However when grouping the benchmarks by $|\mathcal Q|$ and $|\mathcal X|$, see Figure~\ref{fig:b},
we observe good performance of our approach for $|\mathcal Q| = 0$ and $|\mathcal X| \leq 2$ resp. $|\mathcal X| \geq 6$.
Figure~\ref{fig:c} shows that our approach solved 52 problems not solved by the state-of-the-art provers. Notably, while there is big overlap in solved instances, ileanCoP and nanoCoP also have a significant symmetric difference.
\begin{figure}
	\centering
	\begin{tabular}{c|c|lr|lr|lr|lr|c}
		$|\mathcal Q|$&$|\mathcal X|$&\multicolumn{2}{c}{Embedding}&\multicolumn{2}{c}{Embedding (idem.)}&\multicolumn{2}{c}{ileanCoP}&\multicolumn{2}{c}{nanoCoP-i 2.0}&Total\\\hline
		0&0		&157&88.2\%	&157&88.2\%		&128&71.9\%		&61&38.1\%	&178\\
		0&1-2	&119&29.8\%&130&32.5\%		&108&27.0\%		&96&24.0\%	&400\\
		0&3+	&33&18.9\%	&38&21.7\%		&70&40.0\%		&51&29.1\%	&175\\
		1-2&0-2	&84&29.3\%	&81&28.2\%		&227&79.1\%		&221&77.0\%	&287\\
		1-2&3+	&102&24.7\%	&98&27.3\%		&180&43.6\%		&157&39.1\%	&413\\
		3+&0+	&66&5.4\%	&63&5.2\%		&262&20.7\%		&270&22.2\%	&1216\\
	\end{tabular}
	\caption{Solved problems grouped by $|\mathcal Q|$ and $|\mathcal X|$.}
	\label{fig:b}
\end{figure}

>>>>

An important step in the embedding will be the elimination of quantifiers via Herbrandization.
In this process we introduce fresh variables and add additional function symbols to the signature.
A fresh variable is any variable that does not occur in any considered formula.
Whenever we add a function symbol we implicitly extend the signature by a not previously contained symbol.

\begin{definition}\label{definition:skolemization}
	For formulas $\varphi$ we define the Skolemization $\varphi^S_Z$ and Herbrandization $\varphi^H_Z$ with respect to a set of free variables $Z$ by simultaneous induction:
	\begin{itemize}
		\item $A^S_Z = A^H_Z = A$ for each atomic $A$.
		\item $(\varphi\circ\psi)^X_Z = \varphi^X_Z\circ\psi^X_Z$ for $\circ\in\{\wedge, \vee\}$, $X\in\{S, H\}$.
		\item $(\varphi\to\psi)^S_Z = \varphi^H_Z\to \psi^S_Z$ and $(\varphi\to\psi)^H_Z = \varphi^S_Z\to\psi^H_Z$.
		\item $(\forall x\varphi)^S_Z = \forall x(\varphi^S_{Z\cup\{x\}})$.\\$(\forall x\varphi)^H_Z = \varphi[s(z_1,\dots,z_n)/x]^H_Z$ where $s$ is a new function, $\{z_1\dots z_n\} = Z$.
		\item $(\exists x\varphi)^S_Z = \varphi[s(z_1,\dots,z_n)/x]^S_Z$ where $s$ is a new function, $\{z_1\dots z_n\} = Z$.\\$(\exists x\varphi)^H_Z = \exists x(\varphi^H_{Z\cup\{x\}})$.
=======
		\item $(\forall x\varphi)^S_Z = \forall x(\varphi[a/x]^S_{Z\cup\{a\}}[x/a])$ where $a$ is a new free variable.\\$(\forall x\varphi)^H_Z = \varphi[s(z_1,\dots,z_n)/x]^H_Z$ where $s$ is a new function, $\{z_1\dots z_n\} = Z$.
		\item $(\exists x\varphi)^S_Z = \varphi[s(z_1,\dots,z_n)/x]^S_Z$ where $s$ is a new function, $\{z_1\dots z_n\} = Z$.\\$(\exists x\varphi)^H_Z = \exists x(\varphi[a/x]^H_{Z\cup\{a\}}[x/a])$
 where $a$ is a new free variable.
>>>>>>> c8d6f4a7fa194cc08089d36f91f2f60b706bd539
	\end{itemize}
	Let $\varphi^S = (\exists x_1\dots\exists x_n \varphi[x_1/a_1\dots x_n/a_n])^S_\emptyset$ and $\varphi^H = (\forall x_1\dots\forall x_n \varphi[x_1/a_1\dots x_n/a_n])^H_\emptyset$ where $a_1,\dots,a_n$ are the free variables occurring in $\varphi$.
\end{definition}

@@

This is somewhat unsatisfying as we end up in a much more complex logic. However using the normal form from Lemma~\ref{lemma:propositional-normal-form}, i.e. assuming that $\varphi$ is of the form $$\left(\bigwedge\mathcal R\wedge\bigwedge\mathcal X\right)\to P$$ for some flat clauses $\mathcal R$ and implicational clauses $\mathcal X$, further simplification is possible:
\begin{itemize}
	\item For flat clauses $(\bigwedge A_i\to\bigvee B_j)^\nu$ is
	$$\forall w\left(\nu\preceq w\to\bigwedge_i A_i(w)\to\bigvee_jB_j(w)\right).$$
	\item For implication clauses $((A\to B)\to C)^\nu$ is
	$$\forall w(\nu\preceq w\to(\forall k(w\preceq k\to A(k)\to B(k)))\to C(w))$$
\end{itemize}

and after applying Herbrandization we end up with a formula $$\varphi^{CH} = K(\varphi)\to\left(\bigwedge\mathcal R^{b S}\wedge \bigwedge\mathcal X^{b S}\right)\to P(s)$$ where $s$ is a new constant symbol, each formula in $\mathcal R^{b S}$ is of the form
$$\forall w\left(s\preceq w\to\bigwedge_iA_i(w)\to\bigvee_jB_j(w)\right)$$
and each formula $\psi\in\mathcal X^{b S}$ is of the form
$$\forall w(s\preceq w\to(w\preceq f_\psi(w)\to A(f_\psi(w))\to B(f_\psi(w)))\to C(w))$$
with $f_\psi$ being a new function symbol.

\begin{definition}
For $\psi\in\mathcal X$ let $[\psi]$ denote the corresponding clause in $\mathcal X^{b S}$. Suppose we are given a counter-model $\mathcal M = (M, I)$ for $\varphi^{CH}$ such that $m\preceq f_\psi^I(m)$ for each $m\in M$, $\psi\in \mathcal X$.
We say $(A\to B)\to C\in\mathcal X$ is \emph{fulfilled} at $m\in M$ iff $A^I(m)\to B^I(m)$ is false or $C^I(m)$ is true. For $\psi\in\mathcal X$ define $$g_\psi : M\to M, m\mapsto\begin{cases}
		m,&\text{ if $\psi$ is fulfilled at $m$ or $m\not\preceq f^I_{[\psi]}(m)$,}\\
		f^I_{\lbrack\psi\rbrack}(m),&\text{ else.}		
	\end{cases}$$Define a model $\mathcal M_T = (M_T, I_T)$ as follows:
	\begin{itemize}
		\item $M_T$ is the set of sequences without repetition on $\mathcal X$.
		\item $s^{I_T} = \epsilon$.
		\item Interpret $\preceq$ as the prefix-order.
		\item We set $$f_\psi^{I_T}(\psi_1\dots\psi_n) = \begin{cases}
			\psi_1\dots\psi_n, &\text{if $\psi$ occurs in $[\psi_1]\dots[\psi_n]$,}\\
			\psi_1\dots\psi_n\psi, &\text{else.}			
		\end{cases}$$
		\item For propositional variables $P$, we set $$P^{I_T}\left(\psi_1\dots \psi_n\right) = P^I\left(g_{\psi_n}\left(\dots\left(g_{\psi_1}\left(s^I\right)\right)\dots\right)\right).$$
	\end{itemize}
\end{definition}

\begin{lemma}
	Suppose $(M, T)$ is a counter-model to $\varphi^{CH}$, then so is $(M_T, I_T)$.
\end{lemma}
\begin{proof}
	It follows directly from the definitions that $M_T, I_T\not\models P(s)$ and $M_T, I_T\models K(\varphi)$. It is easy to show that $M_T, I_T\models \psi$ for $\psi\in\mathcal R^{bS}$ from persistency. Let $\psi\in\mathcal X^{bS}$, we show $M_T, I_T[\psi_1\dots\psi_n/w] \models s\preceq w\to (w\preceq f_\psi(w)\to A(f_\psi(w)\to B(f_\psi(w)))\to C(w))$ for all $\psi_1\dots\psi_n\in M_T$. Let $\psi_1\dots\psi_n\in M_T$ and $m = g_{\psi_n}(\dots(g_{\psi_1}(s^I))$. If $M, I[m/w]\models C(w)$ we are done. Otherwise $M, I[m/w]\not\models s\preceq w$ or $M, I[m/w]\not\models w\preceq f_\psi(w)\to A(f_\psi(w)) \to B(f_\psi(w))$. The former is impossible since $g_\psi$ is increasing for all $\psi$. For the latter to hold we must have $M, I[m/w]\models w\preceq f_\psi(w)$, $M, I[m/w]\models A(f_\psi(w))$ and $M, I[m/w]\not\models B(f_\psi(w))$. If $\psi$ is fulfilled at $m$ we have $g_\psi(m) = m$, otherwise $g_\psi(m) = f_{[\psi]}^I(m)$. In any case $M, I'[\psi_1\dots\psi_n/w]\models A(f_\psi(w))$ and $M_T, I_T[\psi_1\dots\psi_n/w]\not\models B(f_\psi(w))$. It follows that $M_T, I_T[\psi_1\dots\psi_n/w]\not\models w\preceq f_\psi(w)\to A(f_\psi(w))\to B(f_\psi(w))$ and therefore $M_T, I_T\models \psi$.
=======
	1. If $C^I(m)$ is true then we are done due to persistency. Otherwise $C^I(m)$ is false.
	Because $(A^I(f_{[\psi]}^I(m))\to B^I(f_{[\psi]}^I(m)))\to C^I(m)$ holds, then $A^I(f_{[\psi]}^I(m))\to B^I(f_{[\psi]}^I(m))$ must be false.

	2. Let $n\succeq^I m$.
	If $C^I(n)$ is true, we are done.
	Otherwise $C^I(n)$ is false.
	Due to persistency $C^I(m)$ is also false.
	Because $\psi$ is fulfilled at $m$, $A^I(m)\to B^I(m)$ must be false, i.e. $A^I(m)$ is true and $B^I(m)$ is false. Then $A^I(n)$ and $A^I(f^I_{[\psi]}(n))$ are also true due to persistency.
	Because $(A^I(f^I_{[\psi]}(n))\to B^I(f^I_{[\psi]}(n)))\to C^I(n)$ holds, we now get that  $B^I(f^I_{[\psi]}(n))$ must be false.
	But then due to persistency so is $B^I(n)$ and we have that $\psi$ is fulfilled at $n$.
>>>>>>> c8d6f4a7fa194cc08089d36f91f2f60b706bd539
\end{proof}

@@

\begin{definition}\label{def:fo-translation}
	Let $\varphi$ be a predicate formula. Define $\varphi^{\nu}$ inductively:
\todo{genau genommen müsstest du noch sagen, dass $\nu$ eine freie Variable ist. Im letzten Fall der Definition benützen wir dann aber w gleichzeitig als freie und gebundene Variable}
	\begin{itemize}
		\item $\bot^\nu = \bot$.
		\item $A(\vec t)^{\nu} = A(\vec t, \nu)$ for every predicate symbol $A$.
		\item $(\varphi\circ\psi)^\nu = \varphi^\nu\circ\psi^u$ for $\circ\in\{\wedge, \vee\}$.
		\item $(\varphi\to \psi)^\nu = \forall w(\nu\preceq w\to\varphi^{w}\to\psi^{w})$.
		\item $(\exists x\varphi)^\nu = \exists x(E(x,\nu)\wedge\varphi^\nu)$.
		\item $(\forall x\varphi)^\nu = \forall w(i\preceq w\to \forall x(E(x, w)\to \varphi^w))$ where $w$ is a new bound variable.
	\end{itemize}
	where $w$ is some new bound variable. Let $K(\varphi)$ encode the theory of Kripke structures as well as the predicate $E$, i.e.
	\begin{align*}
		K(\varphi) = \:& \text{PartialOrder}(\preceq) \wedge \forall u \forall w (u\preceq w\to \text{DomainSubset}(u, w)) \wedge\\
		& \forall u(\text{World(u)}\to \text{DomainClosed}(u))\wedge \forall u\forall w (u\preceq w\to \text{Persistent}(u, w)).
	\end{align*}
	with e.g.:\vspace*{-.76cm}
	\begin{align*}
		\text{PartialOrder}(\preceq) = &\:\forall u(u\preceq u)\wedge\forall u\forall w(u\preceq w\to w\preceq u\to u = w)\wedge\\&\:\forall u\forall v\forall w(u\preceq v\to v\preceq w\to u\preceq w)\\
		\text{DomainSubset}(u, w) = &\:\forall x(E(x, u)\to E(x, w))\\
		\text{World}(u) = &\:\exists xE(x, u)\\
		\text{DomainClosed}(u) = &\:\bigwedge\left\{\forall\vec x(\vec E(\vec x, u)\to E(f(\vec x), u))\:|\:\text{$f$ a function in $\varphi$}\right\}\\
		\text{Persistent}(u, w) = &\:\bigwedge\left\{\forall\vec x(\vec A(\vec x, u)\to A(\vec x, w))\:|\:\text{$A$ a predicate in $\varphi$}\right\}
	\end{align*}
	Then define
	$\varphi^C = K(\varphi)\to\text{World}(b)\to \vec E(\vec a, b)\to \varphi^b$ where $\vec a$ contains all free variables occurring in $\varphi$ and $b$ is a new free variable.
\end{definition}

@@

\begin{wrapfigure}[15]{r}{0.4\textwidth}
	\vspace{6.6cm}
	\hspace*{1.5cm}
	\begin{tikzpicture}
		\begin{scope}[opacity=0.1, blend mode=multiply]
			\def\firstcircle{(90:.75) circle (1.5)}
			\def\secondcircle{(210:.75) circle (1.5)}
			\def\thirdcircle{(330:.75) circle (1.5)}
			\begin{tikzpicture}
				\begin{scope}[shift={(3cm,-5cm)}, fill opacity=0.5]
					\fill[red] \firstcircle;
					\fill[green] \secondcircle;
					\fill[blue] \thirdcircle;
					\draw node {$491$};
					\draw node at (30:1.2) {$30$};
					\draw node at (150:1.2) {$42$};
					\draw node at (270:1.2) {$22$};
					\draw node at (90:1.8) {$8$};
					\draw node at (210:1.8) {$2$};
					\draw node at (330:1.8) {$417$};
				\end{scope}
			\end{tikzpicture}
		\end{scope}
	\end{tikzpicture}
	\vspace*{-7.6cm}
	\caption{Instances proven by combinations of Embedding (red), Embedding (idem.) (green), ileanCoP or nanoCoP (blue)}
	\label{fig:c}
\end{wrapfigure}

Two versions of the translation were tested, one with and one without the additional axioms encoding idempotence. The results are stated in Figure \ref{fig:a}. 
In general, our approach falls short of the state of the art. 
=======
\vspace*{-.5cm}
Two versions of the translation were tested, one with and one without the additional axioms encoding idempotence. The results are stated in Figure \ref{fig:a}.
In general, our approach falls short of the state of the art.
>>>>>>> c8d6f4a7fa194cc08089d36f91f2f60b706bd539
However when grouping the benchmarks by $|\mathcal Q|$ and $|\mathcal X|$, see Figure~\ref{fig:b},
we observe good performance of our approach for $|\mathcal Q| = 0$ and $|\mathcal X| \leq 2$ resp. $|\mathcal X| \geq 6$.
Figure~\ref{fig:c} shows that our approach solved 52 problems not solved by the state-of-the-art provers. Notably, while there is big overlap in solved instances, ileanCoP and nanoCoP also have a significant symmetric difference.
\begin{figure}
	\centering
	\begin{tabular}{c|c|lr|lr|lr|lr|c}
		$|\mathcal Q|$&$|\mathcal X|$&\multicolumn{2}{c}{Embedding}&\multicolumn{2}{c}{Embedding (idem.)}&\multicolumn{2}{c}{ileanCoP}&\multicolumn{2}{c}{nanoCoP-i 2.0}&Total\\\hline
		0&0		&157&88.2\%	&157&88.2\%		&128&71.9\%		&61&38.1\%	&178\\
		0&1-2	&119&29.8\%&130&32.5\%		&108&27.0\%		&96&24.0\%	&400\\
		0&3+	&33&18.9\%	&38&21.7\%		&70&40.0\%		&51&29.1\%	&175\\
		1-2&0-2	&84&29.3\%	&81&28.2\%		&227&79.1\%		&221&77.0\%	&287\\
		1-2&3+	&102&24.7\%	&98&27.3\%		&180&43.6\%		&157&39.1\%	&413\\
		3+&0+	&66&5.4\%	&63&5.2\%		&262&20.7\%		&270&22.2\%	&1216\\
	\end{tabular}
	\caption{Solved problems grouped by $|\mathcal Q|$ and $|\mathcal X|$.}
	\label{fig:b}
\end{figure}
